Interisland movements and oceanic swimming of woodland caribou in Newfoundland

### 2020-05-11 paper/manuscript.Rmd
P1

The Fogo Island archipelago, off the coast of Newfoundland, Canada, is home to
approximately 300 woodland caribou. During routine fieldwork on May 30, 2017, we
observed an unmarked adult male caribou swim between two small islands (Figure 1, see Figure 2 for location), a distance of at least 470 m which took ~9 minutes (~52 m
per minute). This observation prompted us to investigate whether swimming
behaviour was common among GPS radio-collared caribou in the population (n = 29, for collaring details see [@Peignier_2019]). Using `r substr(version$version.string, 1, 15)` [@R], we identified
swimming events as two consecutive GPS locations (2-hour relocation rates)  from
an individual occurred on different islands. Northeastern Newfoundland typically
experiences pack ice during winter and caribou are known locally to travel
between islands by walking over the ice. We restricted our GPS data to the
ice-free period of the year (April 1 to December 31) and we identified `r nids`
adult female caribou that collectively had `r nevents` swimming events over
three years (Figure 2). In addition to our own visual and remotely sensed
observations, residents of Fogo Island have also reported observing caribou
swimming between islands on numerous occasions.

>>>>

The Fogo Island archipelago, off the coast of Newfoundland, Canada, is home to
approximately 300 woodland caribou. During routine fieldwork on May 30, 2017, we
observed an unmarked adult male caribou swim between two small islands (Figure
1, see Figure 2 for location), a distance of at least 470 m which took ~9
minutes (~52 m per minute). This observation prompted us to investigate whether
swimming behaviour was common among GPS radio-collared caribou in the population
(n = 29, for collaring details see [@Peignier_2019]). We identified swimming
events as two consecutive GPS locations (2-hour relocation rates)  from an
individual occurred on different islands. Northeastern Newfoundland typically
experiences pack ice during winter and caribou are known locally to travel
between islands by walking over the ice. We restricted our GPS data to the
ice-free period of the year (April 1 to December 31) and identified `r nevents`
swimming events over three years (Figure 2). In addition to our own visual and
remotely sensed observations, residents of Fogo Island have also reported
observing caribou swimming between islands on numerous occasions.
